scoring

### 2022-04-14 darts/scoring.Rmd
quick revisions for fast scoring

---
title: "scoring"
output: html_document
date: '2022-04-13'
---

@@

scores <- function(observed, dat) {
  logsscore <- scoringRules::logs_sample(observed, dat)
  crpsscore <- scoringRules::crps_sample(observed, dat)
  data.frame(logs = mean(logsscore[-1]), crps =  mean(crpsscore[-1]))
}

# Score just the 1st replicate "true" observations
observed <- emp_draws %>%  filter(iter == 0, ensemble==0) %>%  pull(value)
dat <- forecasts %>%  filter(iter == 0, ensemble==0) %>%  select(ensemble, value) %>% as.matrix()
scores(observed, dat)

```
```{r}
# score over all replicates:
all_scores = list()
for (i in (0:4)) {
  for (e in 0:99){
    dat <- forecasts %>%  filter(iter == i, ensemble == e) %>%  select(ensemble, value) %>% as.matrix()
    rep_scores <- emp_draws %>% filter(iter==i) %>%  group_by(ensemble) %>%  group_map(~ scores(.x$value, dat)) %>%  bind_rows()
    all_scores <- append(all_scores, rep_scores)
  }
  print(i)
}

all_scores %>%  summarise(across(.fns= base::mean))

library(patchwork)
ggplot(all_scores) + geom_histogram(aes(crps)) + 
(ggplot(all_scores) + geom_histogram(aes(logs)) )

>>>>

---
title: "scoring"
output: github_document
date: '2022-04-13'
---

```{r}
library(scoringRules)
library(tidyverse)
```

@@

scores <- function(observed, dat) {
  logsscore <- scoringRules::logs_sample(observed, dat)
  crpsscore <- scoringRules::crps_sample(observed, dat)
  data.frame(logs = mean(logsscore[-1]), crps =  mean(crpsscore[-1]))
}
```

```{r}

## Currently it looks like only one tp_model and one ml_model, but 5 iterations:
## We will need to generalize this code to map over multiple tp_models and ml_models etc
# forecasts %>% count(tp_model, ml_model, iter)

## pivot forecast into a matrix of size(time) x size(ensembles)
i <- 1
dat <- forecasts |> filter(iter == i) |>
  select(t = time, i = ensemble, N = value) |> 
 pivot_wider(id_cols = "t", names_from="i", values_from = "N") |> 
  select(-t) |> as.matrix()

test <- emp_draws |> filter(iter == i)  |>
  select(t = time, i = ensemble, N = value)
```

```{r}
bench::bench_time({
rep_scores <- 
  test |> 
  group_by(i) |> 
  group_map(~ scores(.x$N, dat)) |> 
  bind_rows()
})
```

```{r}
library(patchwork)
ggplot(all_scores) + geom_histogram(aes(crps)) + 
(ggplot(all_scores) + geom_histogram(aes(logs)) )
